\section{Discussion}
The discussion is based on an analysis of when each Subject B are in the fight, flight, freeze or tend/befriend state in the broken level. Further observations were also discussed and can be found in Appendix \ref{fo}.

\textbf{Test 1:} The subject raised his eyebrow in surprise and after a short while of asserting the situation quickly ended the level and leaned back away from the tablet, fleeing the task. When he realized that he still had some time left, he moved in to try one more time in an attempt to fight. He makes uncomprehending noises and performs the task very unfocused, and as soon as the time runs out he leans back and away again. 

\textbf{Test 2:} The subject froze when encountering the broken level, and sat very still repeating a circular motion on the tablet, trying not to draw the attention of Subject A. Her face gradually turned more red and she holds back a smile, and when Subject A made his comment she laughed. 

\textbf{Test 3:} His tone rose in pitch and he tried to laugh off the situation he was not comfortable with, which was clear due to the increased color of his face. He fled the situation by defusing the seriousness of the competition with humor.

\textbf{Test 4: }The subject completed the level with little deviation from the path, and in pace, which suggested she attempted to follow the line from memory, disregarding the missing light feedback. When she first lost track of the line, she reached out to the spectator: “It gets--It gets completely red”, which the spectator reacted upon by turning her gaze to her. This situation can be interpreted as a tend/befriend, as they react to the stressful event by socializing. Furthermore, her body language with her leaning back and sitting restless in the chair pointed towards a flight situation. 

\textbf{Test 5:} She kept attempting to find the line, and when it failed, she started over while leaning further towards the tablet with an even more focused expression, signalling annoyance and concentration. She continued to fight and ended up retrying the level three times, which indicated a response of fight.
