\section{Results}
The results consisted of a summary of each session with Subject B in the broken level. The summary was based on the observations made from the video analysis.

\textbf{Session 1}: The subject moved his eyebrows when he encountered the broken level. He attempted to trace the line twice and attempted to follow the line, as he remembered it. When he was unable to find the green light, he exclaims “fuck”, and continued to lift the tangible widget while exhaling, after entering the red circle.

\textbf{Session 2}: When she encountered the broken level she struggled for approx. 10 seconds with little facial response, other than a brief smile. When Subject A then looked at her, she struggled to hold back a smile, until Subject A comments “That’s very red”, after which she erupts with laughter, which intensifies when the score is presented.

\textbf{Session 3}: His voice is higher pitched when he found himself in trouble. He cursed and his face turned more red. When the light turned red he exclaimed “now it is super red” in an agitated voice. He continued to struggle while laughing while previously having a smock expression when he observed Subject A.

\textbf{Session 4}: Subject A comforted and helped Subject B. When unable to remember the line, Subject A tells her to: “Follow the colours”. Subject B had open mouth when she was  moving the tangible widget, but when she lost her path, she closed it with little twitches. She smiled upon giving up and leaned back, afterwards she looked at the timer and leaned back again.

\textbf{Session 5}: The subject furrows her brow in concentration when encountering the broken level. She moves the widget slowly through the whole session, while Subject A is quiet and calm. Deeply concentrated on the task at hand. When the light turns red, she goes back to the beginning and starts over. This is repeated three times.
