\section*{Test Instructions}\label{instr}
\textbf{Introduction in the test room:}
\begin{itemize}
\item Demographics: study, usage of tablets, experience with tangible widgets.
\item Start camera - confirm permission to film
\item We will be leaving the room, so listen carefully 
\item Explain what the game is about
\begin{itemize}
\item Trace the line with widget
\item show where to hold it
\item explain the delay
\item time limit - continues till time runs out, can’t finish earlier
\item focus on accuracy within the time limit “as close to 100\% as possible”
\item “There will first be a tutorial, then a training level and then you will play three real levels that are the “real test””
\item “When the first person is done, switch seats(for the camera) and play through it again” 
\item Explain why two participants
\begin{itemize}
\item Give them paper and explain that they need to fill out the fields so they can compare results
\item facilitate a way to choose who goes first - if they can’t decide by themselves rock paper scissors
\end{itemize}
\item start the game - “When you are both done, come get us, we will be right outside the door”
\item final questions?
\end{itemize}
\end{itemize}

\section*{Semi-structure Interview}\label{semi}
The questions in the post test interview asked to the participants general experience of the game in order to see, if they bring up the subject of the misguiding light feedback. And the last part of the interview reveals the broken level in order to detect how they react on it.
\begin{itemize}
\item “How was it?”
\item General comments
\item “Who won?”
\item Check their map scores
\item “Was it fun?”
\item Take the conversation wherever it leads
\begin{itemize}
\item What did you think of the light feedback?
\item was it easy to trace the line?
\item Did you like interacting with the tangible widget?
\item Did you like
\end{itemize}
\item Reveal gimmick
\begin{itemize}
\item It is actually a different test for a perception and cognition course
\item The last map for the last person was rigged
\item Looking for the reaction at that point
\item Listen to feedback on that / comments on that
\item Thank them for participating
\end{itemize}
\end{itemize}

\section*{Further Observations}\label{fo}
\begin{itemize}
\item Female/male mixed pairs were competitive, while the two females were more inclined to help one another or giving moral support. Some had more attention on the score than. All subjects expressed some sense of relief or relaxation when receiving the score, as their concentration is less focused. 
\item Verbally the subjects expressed themselves by asking questions to themselves or the spectator, by cursing, by giving commands to the light feedback, and by making small uncomprehending sounds. 
\item Some subjects did not speak much while interaction with the game, as they were in full concentration in the task of tracing the line. Instead they made small unconscious facial expressions.
\item All subjects would smile or make small twitches with their mouth while interacting with the system.
\item There is a tendency that Subject B is very curios when Subject A is interacting with the system. This can be to learn the mechanics of the game, learn from Subject A’s mistake, or making their own strategies, as they believe they have the advantage. While Subject A reacted by teasing the other with the score, making suggestions, or by looking away passively.
\end{itemize}
