\section*{Session 3 Table}
\begin{tabular}{|c|c|c|}
\hline 
\textbf{Demographics} & Subjec A & Subject B \\ 
\hline 
Gender & Male  & Female \\ 
\hline 
Sudy & Medialogy 3. Semester & Medialogy 3. Semester \\ 
\hline 
Tablet Use & Every Third Month & Daily \\ 
\hline 
Tangible Widget Experience & Yes, Stylus & Yes, Stylus  \\ 
\hline 
Language & Danish & Danish\\ 
\hline 
Name & Emilie & Kejser\\ 
\hline \hline
Tutorial Level & 100\% & 100\% \\ 
\hline 
Level 1 & 90\% & 82\% \\ 
\hline 
Level 2 & 31\% & 97\% \\ 
\hline 
Level 3 & 67\% & 28\% \\ 
\hline 
\end{tabular} 

Note: No tablet video recording for Subject B, because the subject move the tablet instead of switching chairs. Writing the total score on the scoreboard. A: 188 and B: 207.

\textbf{Interview notes:}
\begin{itemize}
\item The light feedback was gone in the level 2 for Subject A and level 3 for Subject B.
\item Tutorial was easy, they both got 100\%.
\item Subject A: Her dad would move the tangible widget rapidly back and forth in order to hit the line.
\item They tried to track back to the green light, trial and waiting when to turn green again.
\item Teasing a little, “who is the victor”, they start calculating, B wins, they are in the same group, poking a bit to each \item other. Subject B really needs to win, “fuck”.
\item Subject A: is not that competition fixated, but admits that it might be because she started playing instead of ending it. 
\end{itemize}

\textbf{After revealing the test purpose:}
\begin{itemize}
\item Subject B: That explains why I got beaten. Subject A: answers you won anyway.
\item Subject B: Appeals to logic, worked from trial and error. Needed to win this, shit!
\item Subject B: colour blind, red-green efficient not blind.
\item Subject A: looked down in the tablet and not the light (Subject B agrees). Imagined that the level could stop when reaching the goal.
\end{itemize}

